Side-effects

### 2021-08-12 analysis/side-effects.Rmd
WIP: more SE analysis

library(DT)
library(digest)
library(fs)
library(fst)
library(purrr)
library(tidyverse)
library(viridis)
library(xtable)

@@

>>>>

library(DT)
library(digest)
library(dplyr)
library(fs)
library(fst)
library(purrr)
library(readr)
library(stringr)
library(tidyr)
library(viridis)
library(xtable)

@@

```{r}
N <- read_csv(PACKAGE_NORMALIZED_EXPRESSION_FILE) %>%
  select(minimized, expr_resolved_hash=hash)
```

```{r}
E <- read_fst(PACKAGE_SUM_CALLS_FILE) %>% as_tibble()
EN <- left_join(E, N, by="expr_resolved_hash")

#ENS <- left_join(
#  select(EN, eval_call_srcref, minimized, N1=nb_ev_calls), 
#  select(SE, eval_call_srcref, in_envir, class, N2=N), 
#  by="eval_call_srcref"
#)
```

```{r}
EN_sites <- group_by(EN, eval_call_srcref, minimized) %>% summarise(nb_ev_calls=sum(nb_ev_calls)) %>% ungroup
cs_count(EN_sites, minimized)
```

```{r}
cs_count(EN, wt=nb_ev_calls, minimized)
```

```{r}
SEN <- left_join(SE, N, by="expr_resolved_hash")
```
